r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-10-22 r-package/paper2020/paper2020.Rmd
updates paper references

The r5r package has 3 fundamental functions. The `setup_r5()` function builds a 
multimodal transport network used for routing in R<sup>5</sup>. This function 
(1) downloads/updates a compiled R<sup>5</sup> JAR file, tailored for the 
purposes of the package, and stores it locally in the r5r package directory for 
future use; and (2) combines the OSM and GTFS data sets to build a routable 
network object. For fast routing analysis, r5r currently has two functions:

- `travel_time_matrix()`: computes travel time estimates between one or 
multiple origin/destination pairs for a single departure time or for multiple
departure times over a time window. The travel_time_matrix function uses an R5-specific extension to the RAPTOR routing algorithm developed by Conway et al. [@conway2017evidencebased], which provides an efficient and systematic sample of 
multiple departures per minute over a `time_window` set by the user. If the user
passes a `time_window` parameter to the function, r5r will calculate multiple travel 
time matrices departing each minute and return additional information on the percentile distribution of travel times that allows one to grasp service reliability issues.

- `detailed_itineraries()`: computes detailed information on either the
shortest or multiple alternative routes between one or multiple origin/destination
pairs for a single departure time. The output includes detailed information on
route alternatives such as the transport mode, waiting time, travel time and 
distance of each segment of the trip. This function uses an R5-specific extension
to the McRAPTOR routing algorithm to find paths that are optimal or less than
optimal. The specific extension to McRAPTOR to do suboptimal path routing are not documented yet, but a detailed description of base McRAPTOR can be found in Delling et al (2015).

#> incluir essa ref
#> - Delling, D., Pajor, T., & Werneck, R. F. (2015). Round-based public transit routing. Transportation Science, 49(3), 591-604.

@@

To illustrate functionality, the package includes a small sample data set for 
the city of Porto Alegre (Brazil). It includes four files:

- An OSM network in `.pbf` format.
- A public transport network in `GTFS.zip` format.
- The spatial coordinates of points covering the area in `.csv` format.
- The spatial coordinates of some of the city's points of interest.

@@

```{r, message = FALSE}
# load points of interests and set origin and destination
points <- read.csv(file.path(data_path, "poa_points_of_interest.csv"))
origins <- points[c(10, 14),]
destinations <- points[c(12, 15),]

@@

dit <- detailed_itineraries(r5r_core,
                            origins,
                            destinations,
                            mode,
                            departure_datetime,
                            max_walk_dist,
                            shortest_path = FALSE)

>>>>

The r5r package has 3 fundamental functions:

- `setup_r5()`: builds a multimodal transport network used for routing in R<sup>5</sup>. This function (1) downloads/updates a compiled R<sup>5</sup> JAR file, tailored for the purposes of the package, and stores it locally in the r5r package directory for future use; and (2) combines the OSM and GTFS data sets to build a routable network object.

- `travel_time_matrix()`: computes travel time estimates between one or 
multiple origin/destination pairs for a single departure time or for multiple
departure times over a time window. This function uses an R5-specific extension to the RAPTOR routing algorithm developed by Conway et al. [@conway2017evidencebased], which provides an efficient and systematic sample of 
multiple departures per minute over a `time_window` set by the user. If the user
passes a `time_window` parameter to the function, r5r will calculate multiple travel 
time matrices departing each minute and return additional information on the percentile distribution of travel times that allows one to grasp service reliability issues.

- `detailed_itineraries()`: computes detailed information on either the
shortest or multiple alternative routes between one or multiple origin/destination
pairs for a single departure time. The output includes detailed information on
route alternatives such as the transport mode, waiting time, travel time and 
distance of each segment of the trip. This function uses an R5-specific extension
to the McRAPTOR routing algorithm to find paths that are optimal or less than
optimal. The specific extension to McRAPTOR to do suboptimal path routing are not documented yet, but a detailed description of base McRAPTOR can be found in @delling2015roundbased.

@@

To illustrate functionality, the package includes a small sample data set for 
the city of São Paulo (Brazil). It includes three files:

- An OSM network in `.pbf` format.
- A public transport network in `GTFS.zip` format.
- The spatial coordinates of points covering the area in `.csv` format.

@@

```{r, message = FALSE}
data_path <- system.file("extdata/poa", package = "r5r")

r5r_core <- setup_r5(data_path)

# load points of interests and set origin and destination
points <- fread(file.path(data_path, "poa_points_of_interest.csv"))
origins <- points[c(10, 14),]
destinations <- points[c(12, 15),]

@@

dit <- detailed_itineraries(r5r_core,
                            origins = origins,
                            destinations = destinations,
                            mode = mode,
                            departure_datetime = departure_datetime,
                            max_walk_dist = max_walk_dist,
                            max_trip_duration = max_trip_duration,
                            shortest_path = FALSE)
